Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Fixes

\subsection{Grid computing}
Job schedulers like TORQUE \cite{torque} or Condor \cite{condor} have long been used for solving the problem of resource allocation
within a high-performance-computing (HPC) or grid-computing environment.
For the most part, they do not use a two-level scheduling model like we do but
instead operate as a queue for predefined jobs which are run as resources become
available. Machines and job requirements also tend to show more homogeneity
within such environments (for example, the ratio between CPU, memory, and disk),
so the amount of optimization possible with pricing is lower.

@@

\subsection{Economics/pricing in computer systems}
Lottery scheduling

>>>>

\subsection{Grid computing}
Job schedulers like TORQUE \cite{torque}, Condor \cite{condor}, or LFS \cite{LFS} have long been used for solving the problem of resource allocation
within a high-performance-computing (HPC) or grid-computing environment.
For the most part, they do not use a two-level scheduling model like we do but
instead operate as a queue for predefined jobs which are run as resources become
available. Machines and job requirements also tend to show more homogeneity
within such environments (for example, the ratio between CPU, memory, and disk),
so the amount of optimization possible with pricing is lower.

@@

\subsection{Economics/pricing in computer systems}
Lottery scheduling \cite{lottery} is an example of economic principles applied to computer systems. In lottery scheduling, processes or users are assigned a number of lottery tickets, and the scheduler draws a random lottery ticket. The ticket holder is next scheduled or awarded resources. This probabilistic scheduling algorithm solves starvation as each user has a non-zero probability of being selected in each lottery round. Lottery tickets can also be distributed non-uniformly to compensate certain users or boost their chance of scheduling.
